---
title: "Workshop 7 - assignment 3"
author: "Amanda Roberts"
date: "25/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(skimr)
```

## Data set exploration and identifying a business problem (= main question yo solve)

```{r}
coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')

```

**Question**: How can i predict the rating of coffee? (= what factors affect its rating=quality?)

**Subquestions**:

Does altitude affect quality?

Does the place of origin affect its rating (country?, Far?, Owner?)

Are all robusta beans rated low?

What are most acidic coffee beans?

Let's look at data

```{r}
skim(coffee_ratings)
```

Lets look at the ratings boxplot

```{r}
coffee_ratings%>%ggplot(
  aes(total_cup_points)
)+
  geom_boxplot()

coffee_ratings_clean<-coffee_ratings%>%filter(total_cup_points>69)

coffee_ratings%>%ggplot(
  aes(aroma)
)+
  geom_boxplot()

```

Let's explore factors

```{r}
coffee_ratings%>%count(species, sort=TRUE)
coffee_ratings%>%count(variety, sort=TRUE)
```
1. `variety` should be factor!
get rid of NA (remove observations from data set)
2.can i lump up variety categories with low number of observations

fct_lump

```{r}
coffee_ratings_clean<-coffee_ratings_clean%>%
  mutate(variety=as_factor(variety))%>%
filter(!is.na(variety))

coffee_ratings_clean<-coffee_ratings_clean%>%
  mutate(variety=fct_lump_n(
    coffee_ratings_clean$variety,n=4))

coffee_ratings_clean%>%
  count(variety, sort=TRUE)

```


Let's explore relations between total_cup_points and altitude_mean_meters

```{r}
coffee_ratings_clean%>%ggplot(
  aes(x=altitude_mean_meters, y=total_cup_points)
)+
  geom_point()

coffee_ratings_clean%>%ggplot(
  aes(x=altitude_mean_meters, y=total_cup_points)
)+
  geom_smooth(method = lm)

```



